Matching bullets

### 2015-11-17 imaging-paper.Rnw
i thought i had pushed all ...
Sections + removing the grooves

% Quick Intro
Bullet matching is a process in forensic science done to determine whether two bullets were fired from the same gun barrel. This process has broad applicability in terms of the conviction of criminals in the United States criminal justice system. Ballistics identification has long been considered an accepted and reliable procedure, but in the past ten years has undergone some more significant scrutiny. In 2005, in \emph{United States vs. Green}, the court ruled that the expert could not confirm that the bullet casings came from a specific weapon with certainty, but could merely describe other casings which are similar. Further court cases in the late 2000s expressed caution about the use of ballistics identification evidence.

@@

% Statement of the problem

% Methodology
Throughout this section, we will work with images from the James Hamby Consecutively Rifled Ruger Barrel Study \cite{hamby:2009}. Ten consecutively rifled Ruger P-85 pistol barrels were obtained from the manufacturer and fired to produce known test bullets and unknown bullets for comparison.

@@

% Application

% Conclusion

>>>>

\section{Introduction}
Bullet matching is a process in forensic science done to determine whether two bullets were fired from the same gun barrel. This process has broad applicability in terms of the conviction of criminals in the United States criminal justice system. Ballistics identification has long been considered an accepted and reliable procedure, but in the past ten years has undergone some more significant scrutiny. In 2005, in \emph{United States vs. Green}, the court ruled that the expert could not confirm that the bullet casings came from a specific weapon with certainty, but could merely describe other casings which are similar. Further court cases in the late 2000s expressed caution about the use of ballistics identification evidence.

@@

\section{Problem Statement}

\section{Methodology}
Throughout this section, we will work with images from the James Hamby Consecutively Rifled Ruger Barrel Study \cite{hamby:2009}. Ten consecutively rifled Ruger P-85 pistol barrels were obtained from the manufacturer and fired to produce known test bullets and unknown bullets for comparison.

@@

To improve upon the previous algorithm, the first step must be to eliminate the grooves from the images under the assumption that they do not contain relevant information for determining a match. Fortunately, the location and appearance of the grooves in these 2d plots is quite consistent. Because a bullet is scanned groove to groove, the groove should appear within approximately scan points from each end. That is, on y coordinate system ranging from 0 to 1000 as these images, are, the grooves will appear between $y \in \{0, 100\}$ and $y \in \{900, 1000\}$. Hence, the algorith for removing the grooves can be described as follows:

1. Fix an x coordinate value.
2. Remove values from $y \in \{0, 100\}$ and $y \in \{900, 1000\}$.
3. For each y value from 100 to 900, compute a rolling average to smooth out any deviations occurring near the minimums.
4. Determine the minimum in the first half (corresponding to the left groove) and the minimum in the right half (corresponding to the right groove)
5. Remove all y values below the minimum and above the maximum

\section{Application}

\section{Conclusion}
